My title

### 2024-03-28 paper/paper.qmd
update references

@@

| Variable | New Name   | Description                     | Example |
|----------|------------|---------------------------------|---------|
| sex      | sex        | Respondent's gender             | Female  |
| age      | age        | Respondent's age                | 25      |
| HEALTH   | health     | Respondents' health condition   | Good    |
| SATHEALT | AGE        | The age of the respondents      | 23      |
| PHYSHLTH | Phys_Health| Respondents' physical health    | MALE    |

@@

## Source Data

# Model

The goal of our modelling strategy is twofold. Firstly,...

>>>>

This paper begins with an [Introduction] framing the impact of economic downturns on work hours. It is followed by the [Data] section detailing methodology and cleaning efforts. In the [Results], we analyze work hours and nonresponse rates, leading to the [Discussion] on labour market responses to crises, including the impact of COVID-19, and addressing ethical issues. We later acknowledge our paper's Limitations, suggest paths for Future Research, especially on enhancing response rates, and conclude with a synthesis of our insights. The [Appendix] provides further survey information.

@@

| Variable | New Name  | Description                   | Example |
|----------|-----------|-------------------------------|---------|
| sex      | SEX       | Respondent's gender           | Female  |
| age      | AGE       | Respondent's age              | 25      |
| HEALTH   | health    | Respondents' health condition | Good    |
| PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
| MNTLHLTH | ment_days | Days of Respondents' mental health being not good     | 20      |
| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes     |

@@

## Source Data
The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1]. The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook]. One of the variable names `response` is renamed to be more informative (@tbl-use-var).

The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], and `knitr` [@knitr].

[^1]: https://gss.norc.org/documents/stata/GSS_stata.zip

# Model
The goal of our modelling strategy is twofold. Firstly,...
